Team X Manuscript Figures: Aquatic Organisms

### 2021-07-30 App_Nonessential/Maybe_Delete/Concentration data/Risk_Characterization_GlobalData.Rmd

# Hazard Concentration and Alignment Parameters
```{r}
# Choose hazard concentration and confidence intervals
#particles/L
Threshold1 = 0.18 #90000 
Threshold2 = 0.38 #383000
Threshold3 = 0.37 #391000
Threshold4 = 2.08 #1e6

kable(data.frame(
  Category = c("Hazard Concentrations (particles/L)"),
  "Threshold1" = Threshold1,
  "Threshold 2" = Threshold2,
  "Threshold 3" = Threshold3,
  "Threshold 4" = Threshold4))
```

```{r}
# Choose concentration alignment parameters
alpha = 2.5 #(use 1.6 or 2.5)
x2D_set = 5000#100 #upper size range (microns)
x1D_set = 100#1 #lower size range (microns)

kable(data.frame(
  Category = c("Concentration Alignment Parameters"),
  alpha = alpha,
  "lower_size_range_microns" = x1D_set,
  "upper_size_range_microns" = x2D_set))
```

@@

#function to derive correction factor (CF) from Koelmans et al (equation 2)
CFfnx = function(a = alpha, #default alpha from Koelmans et al (2020)
                 x2D = x2D_set, #set detault values to convert ranges to (1-5,000 um) #5mm is upper defuault 
                 x1D = x1D_set, #1 um is lower default size
                 x2M, x1M){

@@

## Exceedances
```{r}
#calculate exceedance
dfADAM_exceedance <- dfADAM %>% 
  mutate(aboveThreshold1 = factor(case_when(
    Conc >= Threshold1 ~ "above Threshold 1",
    Conc < Threshold1 ~ "below Threshold 1",
  )))

#give summary stat for exceedance
exceedance <- dfADAM_exceedance  %>%
  filter(Sample.Type == "sample") %>% 
  dplyr::select(c(Conc, aboveThreshold1)) %>%
  group_by(aboveThreshold1) %>%
  dplyr::summarize(n = n()) %>% 
  mutate(rel.freq = paste0(round(100 * n/sum(n), 0), "%"))

kable(exceedance)
```
## Histogram
```{r}
#generate plot
dfADAM_exceedance %>% 
  filter(Sample.Type == "sample") %>% 
  ggplot(aes(x = Conc, fill = aboveThreshold1))+
  geom_histogram(aes(y = ..count../sum(..count..)),bins = 50, alpha = 0.9, position = "identity") +
  #geom_smooth(stat = 'density') +
  geom_vline(xintercept = Threshold1, linetype = "dashed", color = "red") +
  geom_text(aes(x = Threshold1- 0.5*Threshold1, y = 0.055), label = paste(Threshold1,"particles/L"),  color = "red") +
  geom_text(aes(x = Threshold1- 0.5*Threshold1, y = 0.06), label = ("Threshold1"),  color = "red") +
  geom_text(aes(x = Threshold1+ Threshold1, y = 0.050), label = paste(exceedance$rel.freq[1], "Above Threshold1"), color = "red") +
  scale_x_log10() +
  #coord_cartesian(xlim = c(0,100000000)) +
  # scale_x_continuous(labels = scales::scientific) +
  xlab("Concentration (particles/L)")+
  scale_y_continuous(name = "Relative Density", labels = scales::percent)+
  #scale_fill_discrete(labels = c("Environmental Concentration", "LOEC")) +
  #scale_color_discrete(labels = c("Environmental Concentration", "LOEC")) +
  labs(title = "Histograms of Concentrations in Adam et al 2019 Dataset",
       caption = "Adam et al. 2019 data; all data corrected to 1-5,000 um; nominal particle/L",
       fill = "Env. Conc. or Tox. Conc.",
       color = "Env. Conc. or Tox. Conc.") +
  theme_minimal() +
  theme(legend.position = "none",
    plot.title = element_text(hjust = 0.5, size = 20),
        axis.title = element_text(size = 16),
        axis.text =  element_text(size = 16),
        legend.text = element_text(size =14),
        legend.title = element_blank())
```
## ECDF

```{r}
#ECDF by System
adam %>% 
filter(System != "") %>% 
  ggplot(aes(x = particle.L.master)) + #, color = System))+
  stat_ecdf(geom = "point", size = 1, alpha = 0.7) +
  stat_ecdf(geom = "step", linetype = 'solid', alpha = 0.3, size = 1.5, color = 'azure3') +
  scale_color_manual(values = wes_palette("Darjeeling1"))+
  geom_vline(xintercept = Threshold1, linetype = 'dashed', color = 'green', size = 1.3) +
  geom_vline(xintercept = Threshold2, linetype = 'dashed', color = 'yellow', size = 1.3) +
  geom_vline(xintercept = Threshold3, linetype = 'dashed', color = 	'orange', size = 1.3) +
  geom_vline(xintercept = Threshold4, linetype = 'dashed', color = 	'red', size = 1.3) +
  geom_text(label = "Threshold 1", color = 'green', x = Threshold1, y = 0.15, size = 6)+
  geom_text(label = "Threshold 2", color = 'yellow', x = Threshold2, y = 0.22, size = 6)+
  geom_text(label = "Threshold 3", color = 'orange', x = Threshold3, y = 0.35, size = 6)+
  geom_text(label = "Threshold 4", color = 'red', x = Threshold4, y = 0.45, size = 6)+
  ylab("Cumulative Density") +
  xlab(paste0("Particles/L (" ,x1D_set, " to ", x2D_set, "um)"))+
  scale_y_continuous(labels = scales::percent)+
  coord_trans(x = "log10") +
  scale_x_continuous(breaks = scales::trans_breaks("log10", function(x) 10^x),labels = comma_signif)+
  annotation_logticks(sides = "b")+ #log scale rick marks on bottom
  #theme_minimal() +
  dark_theme_minimal(base_size = 15) +
  labs(title = "Global Surface Water Marine Microplastics Concentrations",
       subtitle = paste("Particles/L corrected to:",x1D_set, "to", x2D_set, "um"),
       caption = paste("Concentration data from Adams et al (2019): 23 studies, 57 sampling locations, n = 377; corrected for size ranges. Alpha = ",alpha))+
  theme(
    plot.title = element_text(hjust = 0.5, size = 18),
        plot.subtitle = element_text(hjust = 0.5, size = 14))
```

@@

#white mode
ECDF_model_occurrence_ADAM_white <- ECDF_model_occurrence_ADAM +
  geom_vline(xintercept = Threshold1, linetype = 'dashed', color = 'red') +
  geom_vline(xintercept = Threshold3, linetype = 'dashed', color = 'red') +
  geom_vline(xintercept = Threshold2, linetype = 'dashed', color = 	'red') +
  geom_text(label = "5% HC: 95% LCL", color = 'red', x = Threshold3, y = 0)+
  geom_text(label = "5% hazard concentration", color = 'red', x = 110, y = 0.03)+
  geom_text(label = "5% HC: 95% UCL", color = 'red', x = Threshold2, y = 0)+
  geom_text(x = 110, y = 0, label = paste(Threshold1,"particles/L"), color = 'red') +  #label for hazard conc
  #geom_hline(yintercept = 0.925, linetype = 'twodash', color = "#A2A475") +
  #geom_text(label = "92.5% samples below 5% HC Mean", x = 4.5, y = 0.94, color = "#A2A475") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 18, face = "bold"),
        plot.subtitle = element_text(hjust = 0.5, size = 12),
        axis.title = element_text(size = 14),
        axis.text = element_text(size = 12),
        legend.title = element_text(size = 14),
        legend.text = element_text(size = 12))
ECDF_model_occurrence_ADAM_white

@@

```{r}
#dark mode
ECDF_model_occurrence_ADAM_dark <- ECDF_model_occurrence_ADAM +
  geom_vline(xintercept = Threshold1, linetype = 'dashed', color = 'red') +
  geom_vline(xintercept = Threshold3, linetype = 'dashed', color = 'red') +
  geom_vline(xintercept = Threshold2, linetype = 'dashed', color = 	'red') +
  geom_text(label = "95% LCL", color = 'red', x = Threshold3, y = 0, size = 5)+
  geom_text(label = "5% HC", color = 'red', x = Threshold1, y = 0, size = 5)+
  geom_text(label = "95% UCL", color = 'red', x = Threshold2, y = 0, size = 5)+
  geom_text(x = Threshold1, y = 0.1, label = paste(Threshold1,"particles/L"), color = 'red', size =5) +  #label for hazard conc
  #geom_hline(yintercept = 0.925, linetype = 'twodash', color = "yellow") +
  #geom_text(label = "92.5%", x = 3.0, y = 0.96, color = "yellow", size = 6) +
  dark_theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5, size = 18, face = "bold"),
        plot.subtitle = element_text(hjust = 0.5, size = 12),
        axis.title = element_text(size = 14),
        axis.text = element_text(size = 12),
        legend.title = element_text(size = 14),
        legend.text = element_text(size = 12))
ECDF_model_occurrence_ADAM_dark
```

>>>>

# Hazard Concentration and Alignment Parameters
```{r}
# Choose hazard concentration and confidence intervals
HC5LCL = 11 #95% lower CLHC5
HC5 = 75.6 #HC5
HC5UCL = 521 #95% upper CL for HC5

kable(data.frame(
  Category = c("Hazard Concentrations (particles/L)"),
  "HC5_95_Lower_CL" = HC5LCL,
  HazardConcentration5 = HC5,
  "HC5_95_Upper_CL" = HC5UCL))
```

```{r}
# Choose concentration alignment parameters
alpha = 2.5 #(use 1.6 or 2.5)
x2D = 5000 #upper size range (microns)
x1D = 1 #lower size range (microns)

kable(data.frame(
  Category = c("Concentration Alignment Parameters"),
  alpha = alpha,
  "lower_size_range_microns" = x1D,
  "upper_size_range_microns" = x2D))
```

@@

#function to derive correction factor (CF) from Koelmans et al (equation 2)
CFfnx = function(a = alpha, #default alpha from Koelmans et al (2020)
                 x2D = 5000, #set detault values to convert ranges to (1-5,000 um) #5mm is upper defuault 
                 x1D = 1, #1 um is lower default size
                 x2M, x1M){

@@

```{r}
#calculate exceedance
dfADAM_exceedance <- dfADAM %>% 
  mutate(aboveHC5 = factor(case_when(
    Conc >= HC5 ~ "above HC5",
    Conc < HC5 ~ "below HC5",
  )))

#give summary stat for exceedance
exceedance <- dfADAM_exceedance  %>%
  filter(Sample.Type == "sample") %>% 
  dplyr::select(c(Conc, aboveHC5)) %>%
  group_by(aboveHC5) %>%
  dplyr::summarize(n = n()) %>% 
  mutate(rel.freq = paste0(round(100 * n/sum(n), 0), "%"))

kable(exceedance)
```

```{r}
#generate plot
dfADAM_exceedance %>% 
  filter(Sample.Type == "sample") %>% 
  ggplot(aes(x = Conc, fill = aboveHC5))+
  geom_histogram(aes(y = ..count../sum(..count..)),bins = 50, alpha = 0.9, position = "identity") +
  #geom_smooth(stat = 'density') +
  geom_vline(xintercept = HC5, linetype = "dashed", color = "red") +
  geom_text(aes(x = HC5- 0.5*HC5, y = 0.055), label = paste(HC5,"particles/L"),  color = "red") +
  geom_text(aes(x = HC5- 0.5*HC5, y = 0.06), label = ("HC5"),  color = "red") +
  geom_text(aes(x = HC5+ HC5, y = 0.050), label = paste(exceedance$rel.freq[1], "Above HC5"), color = "red") +
  scale_x_log10() +
  #coord_cartesian(xlim = c(0,100000000)) +
  # scale_x_continuous(labels = scales::scientific) +
  xlab("Concentration (particles/L)")+
  scale_y_continuous(name = "Relative Density", labels = scales::percent)+
  #scale_fill_discrete(labels = c("Environmental Concentration", "LOEC")) +
  #scale_color_discrete(labels = c("Environmental Concentration", "LOEC")) +
  labs(title = "Histograms of Concentrations in Adam et al 2019 Dataset",
       caption = "Adam et al. 2019 data; all data corrected to 1-5,000 um; nominal particle/L",
       fill = "Env. Conc. or Tox. Conc.",
       color = "Env. Conc. or Tox. Conc.") +
  theme_minimal() +
  theme(legend.position = "none",
    plot.title = element_text(hjust = 0.5, size = 20),
        axis.title = element_text(size = 16),
        axis.text =  element_text(size = 16),
        legend.text = element_text(size =14),
        legend.title = element_blank())
```

```{r}
#ECDF by System
adam %>% 
filter(System != "") %>% 
  ggplot(aes(x = particle.L.master, color = System))+
  stat_ecdf(geom = "point", size = 2) +
  stat_ecdf(geom = "step", linetype = 'solid', alpha = 0.6, size = 1.5) +
  scale_color_manual(values = wes_palette("Darjeeling1"))+
  geom_vline(xintercept = HC5, linetype = 'dashed', color = 'red') +
  geom_vline(xintercept = HC5LCL, linetype = 'dashed', color = 'red') +
  geom_vline(xintercept = HC5UCL, linetype = 'dashed', color = 	'red') +
  geom_text(label = "95% LCL", color = 'red', x = log10(13), y = 0.15)+
  geom_text(label = paste("HC5:",HC5, "particles/L"), color = 'red', x = log10(105), y = 0.07)+
  geom_text(label = "95% UCL", color = 'red', x = log10(440), y = 0.15)+
  ylab("Cumulative Density") +
  xlab("Particles/L (1-5,000 um)")+
  scale_y_continuous(labels = scales::percent)+
  scale_x_continuous(trans = "log10") +
  annotation_logticks(sides = "b")+ #log scale rick marks on bottom
  theme_minimal() +
  labs(title = "Global Concentrations ECDF by System",
       subtitle = "Particles/L corrected to 1-5,000 um",
       caption = "Concentration data from Adams et al (2019); corrected for size via Koelmans. Hazard Concentration from Koelmans et al (2020)")+
  theme(plot.title = element_text(hjust = 0.5, size = 18),
        plot.subtitle = element_text(hjust = 0.5, size = 14))
```

@@

#white mode
ECDF_model_occurrence_ADAM_white <- ECDF_model_occurrence_ADAM +
  geom_vline(xintercept = HC5, linetype = 'dashed', color = 'red') +
  geom_vline(xintercept = HC5LCL, linetype = 'dashed', color = 'red') +
  geom_vline(xintercept = HC5UCL, linetype = 'dashed', color = 	'red') +
  geom_text(label = "5% HC: 95% LCL", color = 'red', x = HC5LCL, y = 0)+
  geom_text(label = "5% hazard concentration", color = 'red', x = 110, y = 0.03)+
  geom_text(label = "5% HC: 95% UCL", color = 'red', x = HC5UCL, y = 0)+
  geom_text(x = 110, y = 0, label = paste(HC5,"particles/L"), color = 'red') +  #label for hazard conc
  #geom_hline(yintercept = 0.925, linetype = 'twodash', color = "#A2A475") +
  #geom_text(label = "92.5% samples below 5% HC Mean", x = 4.5, y = 0.94, color = "#A2A475") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 18, face = "bold"),
        plot.subtitle = element_text(hjust = 0.5, size = 12),
        axis.title = element_text(size = 14),
        axis.text = element_text(size = 12),
        legend.title = element_text(size = 14),
        legend.text = element_text(size = 12))
ECDF_model_occurrence_ADAM_white

@@

```{r}
#dark mode
ECDF_model_occurrence_ADAM_dark <- ECDF_model_occurrence_ADAM +
  geom_vline(xintercept = HC5, linetype = 'dashed', color = 'red') +
  geom_vline(xintercept = HC5LCL, linetype = 'dashed', color = 'red') +
  geom_vline(xintercept = HC5UCL, linetype = 'dashed', color = 	'red') +
  geom_text(label = "95% LCL", color = 'red', x = HC5LCL, y = 0, size = 5)+
  geom_text(label = "5% HC", color = 'red', x = HC5, y = 0, size = 5)+
  geom_text(label = "95% UCL", color = 'red', x = HC5UCL, y = 0, size = 5)+
  geom_text(x = HC5, y = 0.1, label = paste(HC5,"particles/L"), color = 'red', size =5) +  #label for hazard conc
  #geom_hline(yintercept = 0.925, linetype = 'twodash', color = "yellow") +
  #geom_text(label = "92.5%", x = 3.0, y = 0.96, color = "yellow", size = 6) +
  dark_theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5, size = 18, face = "bold"),
        plot.subtitle = element_text(hjust = 0.5, size = 12),
        axis.title = element_text(size = 14),
        axis.text = element_text(size = 12),
        legend.title = element_text(size = 14),
        legend.text = element_text(size = 12))
ECDF_model_occurrence_ADAM_dark
```

### 2021-07-30 App_Nonessential/Shiny_Manuscript_Figures/Manuscript_Figures.Rmd

```{r collapsible tree example}

@@

```{r endpoints and organism groups, fig.width = 15}
library(viridis)
a <- aoc_setup %>% 
  filter(effect_f != "NA") %>%
  count(lvl1_f, org_f) %>% #how many obs of each organism group within each lvl1
  group_by(lvl1_f) %>%
  mutate(n_lvl1 = sum(n)) %>% #how many obs within each lvl1
  ungroup() %>%   
  ggplot(aes(x = fct_reorder(lvl1_f, n_lvl1), y = n, group = n, fill = org_f)) +
  geom_bar(stat = "identity", position = position_dodge2(preserve = "single"), color = "black", width = 1) +
  scale_x_discrete(labels = function(x) stringr::str_wrap(x, width = 10)) +
  scale_y_continuous(expand = c(0,0)) +
  scale_fill_manual(values= wes_palette("Zissou1", type = "continuous", 13)) +
  theme_classic() +
  theme(text = element_text(size = 16))+
  labs(y = "Number of Endpoints in Database", x = "Endpoint Category", fill = "Organism\nGroup")

@@

```{r particle characteristics}

>>>>

```{r collapsible tree example, include=FALSE}

@@

```{r endpoints and organism groups, fig.width = 15, include=FALSE}
library(viridis)
a <- aoc_setup %>% 
  filter(effect_f != "NA") %>%
  count(lvl1_f, org_f) %>% #how many obs of each organism group within each lvl1
  group_by(lvl1_f) %>%
  mutate(n_lvl1 = sum(n)) %>% #how many obs within each lvl1
  ungroup() %>%   
  ggplot(aes(x = fct_reorder(lvl1_f, n_lvl1), y = n, group = n, fill = org_f)) +
  geom_bar(stat = "identity", position = position_dodge2(preserve = "single"), color = "black", width = 1) +
  scale_x_discrete(labels = function(x) stringr::str_wrap(x, width = 10)) +
  scale_y_continuous(expand = c(0,0)) +
  scale_fill_manual(values= wes_palette("Zissou1", type = "continuous", 13)) +
  theme_classic() +
  theme(text = element_text(size = 16))+
  labs(y = "Number of Endpoints in Database", x = "Endpoint Category", fill = "Organism\nGroup")

@@

```{r particle characteristics, include=FALSE}
